---
title: "diagnostics"
author: "Dine Mamadou"
date: "2/20/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#do '##' to start a new slide
```

##Test

```{r load_things, message=FALSE, echo=TRUE}
library(ggfortify)
library(tidyverse)

my_cars_data <- read_csv("../data/my_data.csv")
head(my_cars_data)

```

##Model

``` {r model, echo=TRUE, results='asis'}
mod1 <- lm(mpg ~ wt, data = mtcars)
summary(mod1)

```

##Assumptions
```{r, fig.width=8}
mtcars %>%
  ggplot(., aes(x = wt, y = mpg)) +
  geom_point() +
  geom_smooth()

```

##The means of the residuals

```{r}
mean(mod1$residuals)
summary(mod1)

```

##Homoskedasticity
```{r}
autoplot(mod1, which = c(1, 3))

```

##Autocorrelation
```{r}
acf(mod1$residuals) 
lmtest::dwtest(mod1)
```

##Normality of Residuals
```{r}
autoplot(mod1, which = 2) 
autoplot(mod1)
```
## Section 1 

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

